\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-31 paper/paper.tex
abstract language fixes

\maketitle
\begin{abstract}
With are more and more devices that are equipped with GPS and generate trajectory data analyzing and using this data catches attention increasingly. That is why besides using some specialized trajectory processing systems for that kind of data the interest in using common databases, especially columnar in-memmory systems, for this task rises. We compare three different data layouts for such databases based on a real-world usecase. Therefore we developed an example application with taxi data and benchmarked our those data layouts against typical queries of our usecase.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
With a strongly increasing number of GPS equipped devices that generate trajectory information, analyzing and using this data catches more and more attention. That is why besides using some specialized trajectory processing systems for that kind of data the interest in using common databases for this task rises. This is the case especially for columnar in-memmory systems. We compare three different data layouts which are designed such databases based on a real-world usecase. Therefore we developed an example application with taxi data and benchmarked those data layouts against typical queries of our usecase.
\end{abstract}
